Adopting the Euro: a Synthetic Control Approach \\ Online Appendix\\ \vspace{2em}

### 2024-01-29 Text/Manuscript.tex
Change text

Finally, this paper closely relates to the recent literature about the euro adoption using the synthetic control approach \citep{Fernandez2015, Verstegen2017, Gasparotti2019}. We build directly on the work of \cite{Puzzello2018} by extending their analysis from six to the twelve member states that joined the Eurozone before 2007. This paper further adds to the existing literature by analysing the main drivers of the economic gains and losses of the euro accession. In particular, our results show that for the majority of Eurozone countries, adopting the euro spurred government consumption and trade while deterred investment and private consumption.

@@

Moreover, the set of predictors used is based on \cite{Abadie2003} and \cite{Born2019}. These predictors are the average GDP shares of private consumption, government consumption, investment, exports, imports, the employed share of the population, the labor productivity growth, the real GDP and its lags.\footnote{We avoid the so-called cherry-picking problem in \cite{Ferman2017} by choosing a standard set of predictors based on previous empirical literature.}

Formally, let $\vec{x_1}$ denote the ($37 \times 1$) vector of $30$ observations for real GDP (including its 29 lags) and $7$ covariates' averages in each Eurozone country (over the pre-treatment period) and let $\vec{X_0}$ denote a ($37 \times 14$) matrix with observations from the donor countries. Finally, let $\vec{w}$ denote a ($14 \times 1$) vector of weights $w_i, \ i=2,...,15$. Then, the optimal weighting scheme is defined by $\vec{w^*}$ which minimizes the following mean squared error:

@@

%Thus, we minimize equation \ref{EQ_min} over the pre-treatment period: from 1970 until 1998 (2000 for Greece) in our baseline specification. We allow for a possible effect of the treatment starting after the Eurozone accession by each country.

@@

\begin{figure}[h!]
    \centering
    \caption{The Impact of the Eurozone Accession}
    \includegraphics[scale=1.15]{SCM_gdp_Annual.pdf}
    \annote{In each graph, the dashed line represents the normalized real GDP for the synthetic country and the continuous line represents the series for the actual country. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. The vertical line represents the treatment period - 1999 for all countries except for Greece which is 2001. For each country, the analysis starts in 1970 and ends in 2007. %The baseline specification has as predictors labor productivity growth, employment share, and GDP shares from PENN Tables 9.1 data. OECD restricted donor pool.
    }
    \label{F_1}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \caption{In-time Placebo Tests}
    \includegraphics[scale=1.2]{}
    \annote{In each graph, the blue dashed line represents the normalized real GDP for the synthetic country and the black full line represents the series for the actual country. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. The vertical line depicts the placebo treatment period - 1992 for all countries. For all countries, the analysis starts in 1970 and ends in 2007. %The baseline specification has as predictors labor productivity growth, employment share, and GDP shares from PENN Tables 9.1 data. OECD restricted donor pool.
    }
    \label{F_Maastricht}
\end{figure}

@@

\section{Appendix}
\subsection{Variables Description and Source}
\begin{table}[!htbp] 
\centering
\footnotesize
\caption{\label{TA_Description} Variables Description}\centering\medskip
\begin{tabular}{p{2cm}p{9cm}p{3.5cm}}
\hline
%rgdpna rconna rdana rnna wa_pop_s emp pop
 Variable code & Description & Source \\ 
 \hline \hline
 rgdpna & Real gross domestic product at constant 2011 national prices in million 2011 US dollars normalized to unity in 1970. & PWT 9.1 \\ \hline
 %rconna & Real consumption at constant 2011 national prices in million 2011 US dollars.  & PWT 9.1 \\ \hline
 %rdana & Real domestic absorption at constant 2011 national prices in million 2011 US dollars.  & PWT 9.1 \\ \hline
 %rinvna & Investment at constant 2011 national prices in million 2011 US dollars computed by subtracting rconna to rdana. & PWT 9.1 \\ \hline
 %rnxna & Net exports of goods and services at constant 2011 national prices in million 2011 US dollars computed by subtracting rdana to rgdpna & PWT 9.1 \\ \hline
 %rgovna & Real government consumption at constant 2011 national prices in million 2011 US dollars. In order to compute this variable one needs to use the share of government consumption in current PPPs (csh\_g) to obtain a series for government consumption in current PPPS cgovn=((csh\_g/(csh\_g+csh\_c))*ccon). Then, in order to adjust for constant PPPs obtain the deflator of total consumption (rconna/ccon) and multiply it by cgovn. & PWT 9.1 \\ \hline
 pop & Total population in millions. & PWT 9.1  \\ \hline
 rgdpnapc & Per head real gross domestic product at constant 2011 national prices in 2011 US dollars computed by dividing rgdpna by pop normalized to unity in 1970. & PWT 9.1 \\ \hline
 rgdpepc & Per head (expenditure side) real gross domestic product at chained PPPs 2011 US dollars computed by dividing rgdpe by pop normalized to unity in 1970. & PWT 9.1 \\ \hline
 emp & Total employment - number of persons engaged in millions. & PWT 9.1\\ \hline
 csh\_prod & Labor productivity growth computed by taking the log-difference between real gdp and total employment & PWT 9.1 \\ \hline
 csh\_emp & Employment share - ratio between total employment and total population & PWT 9.1 \\ \hline
 csh\_c & Private consumption expenditure (\% of GDP) obtained by subtracting general government final consumption expenditure to the series of final consumption expenditure & World Bank \\ \hline
 csh\_g & General government final consumption expenditure (\% of GDP) & World Bank \\ \hline
 csh\_i & Gross fixed capital formation (\% of GDP) & World Bank \\ \hline
 csh\_x & Exports of goods and services (\% of GDP) & World Bank \\ \hline
 csh\_m & Imports of goods and services (\% of GDP) & World Bank \\ \hline
 gnipc &  Gross national income per capita & World Bank \\
 inflation & Inflation rate (\%), Counsumer Price Index of All Commodities& IMF IFS \\ \hline
 Bonds & Long-Term Government Bond Yields, Percent per annum & \cite{Arvai2023} \\ \hline
 %unemp  & Unemployment Rate (\%)                    & World Bank \\ \hline

@@

Share of Priv. Consumption &     56.27 &     51.57 \\  
Share of Gov. Consumption &     17.91 &     20.58 \\  
Share of Investment &     26.53 &     26.27 \\  
Share of Imports &     32.57 &     32.35 \\  
Share of Exports &     31.85 &     33.93 \\  
Employment Share &     45.16 &     48.33 \\  
Labor productivity growth &      2.47 &      2.07 \\  \hline

@@

Share of Priv. Consumption &     54.14 &     54.15 \\  
Share of Gov. Consumption &     21.41 &     20.59 \\  
Share of Investment &     22.87 &     24.74 \\  
Share of Imports &     53.80 &     36.03 \\  
Share of Exports &     55.39 &     36.55 \\  
Employment Share &     38.01 &     49.41 \\  
Labor productivity growth &      2.33 &      1.57 \\  \hline

@@

Share of Priv. Consumption &     52.51 &     52.30 \\  
Share of Gov. Consumption &     19.38 &     19.96 \\  
Share of Investment &     26.66 &     26.54 \\  
Share of Imports &     26.57 &     26.66 \\  
Share of Exports &     28.02 &     27.86 \\  
Employment Share &     47.26 &     47.22 \\  
Labor productivity growth &      3.08 &      1.87 \\  \hline

@@

Share of Priv. Consumption &     55.16 &     56.10 \\  
Share of Gov. Consumption &     21.24 &     19.47 \\  
Share of Investment &     23.11 &     23.42 \\  
Share of Imports &     20.54 &     21.50 \\  
Share of Exports &     21.03 &     22.51 \\  
Employment Share &     40.49 &     43.80 \\  
Labor productivity growth &      2.20 &      1.23 \\   \hline

@@

Share of Priv. Consumption &     57.15 &     57.29 \\  
Share of Gov. Consumption &     19.68 &     18.18 \\  
Share of Investment &     24.50 &     24.30 \\  
Share of Imports &     21.40 &     21.25 \\  
Share of Exports &     20.06 &     21.48 \\  
Employment Share &     48.36 &     48.23 \\  
Labor productivity growth &      2.41 &      1.48 \\  \hline

@@

Share of Priv. Consumption &     63.06 &     60.84 \\  
Share of Gov. Consumption &     16.75 &     17.21 \\  
Share of Investment &     26.46 &     22.76 \\  
Share of Imports &     21.77 &     17.88 \\  
Share of Exports &     15.50 &     17.07 \\  
Employment Share &     38.77 &     45.51 \\  
Labor productivity growth &      1.69 &      1.21 \\  \hline

@@

Share of Imports &     52.85 &     34.67 \\  
Share of Exports &     51.30 &     30.59 \\  

@@

Labor productivity growth &      3.43 &      2.14 \\  \hline

@@

Share of Priv. Consumption &     59.00 &     58.72 \\  
Share of Gov. Consumption &     17.55 &     17.63 \\  

@@

Share of Imports &     19.28 &     19.37 \\  
Share of Exports &     19.86 &     19.86 \\  
Employment Share &     38.25 &     44.11 \\  
Labor productivity growth &      2.48 &      1.24 \\  \hline

@@

Share of Priv. Consumption &     48.16 &     58.05 \\  
Share of Gov. Consumption &     15.33 &     10.82 \\  
Share of Investment &     22.57 &     29.26 \\  
Share of Imports &     81.83 &     39.32 \\  
Share of Exports &     95.78 &     41.20 \\  
Employment Share &     46.63 &     51.00 \\  
Labor productivity growth &      1.81 &      1.54 \\  \hline

@@

Share of Priv. Consumption &     50.90 &     54.78 \\  
Share of Gov. Consumption &     21.94 &     18.40 \\  
Share of Investment &     22.62 &     26.16 \\  
Share of Imports &     47.47 &     37.62 \\  
Share of Exports &     52.01 &     38.27 \\  

@@

Labor productivity growth &      1.56 &      1.48 \\  \hline

@@

Share of Priv. Consumption &     66.93 &     65.45 \\  
Share of Gov. Consumption &     14.03 &     13.91 \\  
Share of Investment &     26.93 &     21.36 \\  
Share of Imports &     31.16 &     21.84 \\  
Share of Exports &     23.27 &     21.12 \\  
Employment Share &     41.81 &     38.57 \\  
Labor productivity growth &      2.02 &      1.29 \\   \hline

@@

Share of Priv. Consumption &     63.12 &     61.46 \\  
Share of Gov. Consumption &     14.51 &     14.58 \\  
Share of Investment &     23.78 &     23.82 \\  
Share of Imports &     18.55 &     17.34 \\  
Share of Exports &     17.13 &     17.47 \\  
Employment Share &     35.38 &     43.58 \\  
Labor productivity growth &      2.56 &      1.10 \\  \hline

@@

\annote{Predictors' means for each country during the pre-treatment period. All numbers are in percent. Variables definitions can be find in Table \ref{TA_Description}.}

@@

>>>>

Finally, this paper closely relates to the recent literature about the euro adoption using the synthetic control approach \citep{Fernandez2015, Verstegen2017, Gasparotti2019} but makes three important contributions. First, we build directly on the work of \cite{Puzzello2018} by extending their analysis from six to the twelve member states that joined the Eurozone before 2007. This contributes to a comprehensive picture of the macroeconomic effects of the Euro accession.

Second, this paper further adds to the existing literature by unpacking the results of the economic gains and losses of the euro accession. In particular, our results show that, for the majority of Eurozone countries, adopting the euro deterred investment and private consumption, but spurred trade and government consumption. There seems to be a negative link between fiscal spending before and after the Euro adoption. Most countries in the sample implemented spending-based austerity measures after the Maastricht Treaty in line with the Stability and Growth Pact (SGP) \citep{Alesina2019}. This has likely created fiscal space which together with access to cheaper credit promoted an increase in government consumption beyond what would have happened absent the Euro adoption. For the few countries that did not consolidate spending before the Euro accession. government consumption was lower than without the Euro.

Third, this paper adds the drivers of Ireland's large economic gains following the Euro adoption. When extending the baseline analysis to the Gross National Income (GNI),  Ireland's economic gains from the Euro adoption, though still positive, become more modest. This means that the large Irish economic gains measured by GDP are closely related to the activities of these multinational corporations that contribute significantly more to GDP--through the production and services rendered within the country--than to GNI, as a large portion of their profits are repatriated to foreign investors or parent companies abroad.

@@

Moreover, the set of predictors used is based on \cite{Abadie2003} and \cite{Born2019}. These predictors are the average GDP shares of private consumption, government consumption, investment, exports, imports, the employed share of the population, the labor productivity growth, the inflation rate, the real GDP and its lags.\footnote{We avoid the so-called cherry-picking problem in \cite{Ferman2017} by choosing a standard set of predictors based on previous empirical literature.}

Formally, let $\vec{x_1}$ denote the ($37 \times 1$) vector of $30$ observations for real GDP (including its 29 lags) and $8$ covariates' averages in each Eurozone country (over the pre-treatment period) and let $\vec{X_0}$ denote a ($38 \times 14$) matrix with observations from the donor countries. Finally, let $\vec{w}$ denote a ($14 \times 1$) vector of weights $w_i, \ i=2,...,15$. Then, the optimal weighting scheme is defined by $\vec{w^*}$ which minimizes the following mean squared error:

@@

@@

\begin{figure}[h!]
    \centering
    \caption{The Impact of the Eurozone Accession}
    \includegraphics[scale=1.15]{SCM_gdp_Annual.pdf}
    \annote{In each graph, the dashed line represents the normalized real GDP for the synthetic country and the continuous line represents the series for the actual country. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. The vertical line represents the treatment period - 1999 for all countries except for Greece which is 2001. For each country, the analysis starts in 1970 and ends in 2007.
    }
    \label{F_1}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \caption{In-time Placebo Tests}
    \includegraphics[scale=1.2]{Output/Figures/SCM_normgdp_s_Rob_1992_Annual.pdf}
    \annote{In each graph, the blue dashed line represents the normalized real GDP for the synthetic country and the black full line represents the series for the actual country. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. The vertical line depicts the placebo treatment period - 1992 for all countries. For all countries, the analysis starts in 1970 and ends in 2007. %The baseline specification has as predictors labor productivity growth, employment share, and GDP shares from PENN Tables 9.1 data. OECD restricted donor pool.
    }
    \label{F_Maastricht}
\end{figure}

@@

\section{Appendix}
\subsection{Variables Description and Source}
\begin{table}[!htbp] 
\centering
\footnotesize
\caption{\label{TA_Description} Variables Description}\centering\medskip
\begin{tabular}{p{2cm}p{9cm}p{3.5cm}}
\hline
%rgdpna rconna rdana rnna wa_pop_s emp pop
 Variable code & Description & Source \\ 
 \hline \hline
 rgdpna & Real gross domestic product at constant 2011 national prices in million 2011 US dollars normalized to unity in 1970. & PWT 9.1 \\ \hline
 %rconna & Real consumption at constant 2011 national prices in million 2011 US dollars.  & PWT 9.1 \\ \hline
 %rdana & Real domestic absorption at constant 2011 national prices in million 2011 US dollars.  & PWT 9.1 \\ \hline
 %rinvna & Investment at constant 2011 national prices in million 2011 US dollars computed by subtracting rconna to rdana. & PWT 9.1 \\ \hline
 %rnxna & Net exports of goods and services at constant 2011 national prices in million 2011 US dollars computed by subtracting rdana to rgdpna & PWT 9.1 \\ \hline
 %rgovna & Real government consumption at constant 2011 national prices in million 2011 US dollars. In order to compute this variable one needs to use the share of government consumption in current PPPs (csh\_g) to obtain a series for government consumption in current PPPS cgovn=((csh\_g/(csh\_g+csh\_c))*ccon). Then, in order to adjust for constant PPPs obtain the deflator of total consumption (rconna/ccon) and multiply it by cgovn. & PWT 9.1 \\ \hline
 pop & Total population in millions. & PWT 9.1  \\ \hline
 rgdpnapc & Per head real gross domestic product at constant 2011 national prices in 2011 US dollars computed by dividing rgdpna by pop normalized to unity in 1970. & PWT 9.1 \\ \hline
 rgdpepc & Per head (expenditure side) real gross domestic product at chained PPPs 2011 US dollars computed by dividing rgdpe by pop normalized to unity in 1970. & PWT 9.1 \\ \hline
 emp & Total employment - number of persons engaged in millions. & PWT 9.1\\ \hline
 csh\_prod & Labor productivity growth computed by taking the log-difference between real gdp and total employment & PWT 9.1 \\ \hline
 csh\_emp & Employment share - ratio between total employment and total population & PWT 9.1 \\ \hline
 csh\_c & Private consumption expenditure (\% of GDP) obtained by subtracting general government final consumption expenditure to the series of final consumption expenditure & World Bank \\ \hline
 csh\_g & General government final consumption expenditure (\% of GDP) & World Bank \\ \hline
 csh\_i & Gross fixed capital formation (\% of GDP) & World Bank \\ \hline
 csh\_x & Exports of goods and services (\% of GDP) & World Bank \\ \hline
 csh\_m & Imports of goods and services (\% of GDP) & World Bank \\ \hline
 gnipc &  Gross national income per capita & World Bank \\ \hline
 inflation & Inflation rate (\%), Counsumer Price Index of All Commodities& IMF IFS \\ \hline
 Bonds & Long-Term Government Bond Yields, Percent per annum & \cite{Arvai2023} \\ \hline
 %unemp  & Unemployment Rate (\%)                    & World Bank \\ \hline

@@

Share of Priv. Consumption &     56.27 &     54.55 \\  
Share of Investment &     26.53 &     26.01 \\  
Share of Gov. Consumption &     17.91 &     17.39 \\  
Share of Imports &     32.57 &     35.91 \\  
Share of Exports &     31.85 &     33.86 \\  
Employment Share &     45.16 &     48.26 \\  
Labor productivity growth &      2.32 &      1.34 \\  
Inflation Rate &      4.24 &      5.16 \\    \hline

@@

Share of Priv. Consumption &     54.14 &     54.45 \\  
Share of Investment &     22.87 &     28.49 \\  
Share of Gov. Consumption &     21.41 &     14.42 \\  
Share of Imports &     53.80 &     41.32 \\  
Share of Exports &     55.39 &     38.67 \\  
Employment Share &     38.01 &     50.64 \\  
Labor productivity growth &      2.19 &      1.46 \\  
Inflation Rate &      4.85 &      4.84 \\  \hline

@@

Share of Priv. Consumption &     52.51 &     53.92 \\  
Share of Investment &     26.66 &     25.07 \\  
Share of Gov. Consumption &     19.38 &     20.13 \\  
Share of Imports &     26.57 &     27.70 \\  
Share of Exports &     28.02 &     26.81 \\  
Employment Share &     47.26 &     47.27 \\  
Labor productivity growth &      2.99 &      2.04 \\  
Inflation Rate &      6.73 &      6.72 \\    \hline

@@

Share of Priv. Consumption &     55.16 &     55.12 \\  
Share of Investment &     23.11 &     23.17 \\  
Share of Gov. Consumption &     21.24 &     20.67 \\  
Share of Imports &     20.54 &     24.60 \\  
Share of Exports &     21.03 &     23.56 \\  
Employment Share &     40.49 &     44.53 \\  
Labor productivity growth &      2.11 &      1.16 \\  
Inflation Rate &      6.22 &     11.96 \\   \hline

@@

Share of Priv. Consumption &     57.15 &     57.23 \\  
Share of Investment &     24.50 &     26.13 \\  
Share of Gov. Consumption &     19.68 &     14.94 \\  
Share of Imports &     21.40 &     36.07 \\  
Share of Exports &     20.06 &     34.36 \\  
Employment Share &     48.36 &     49.49 \\  
Labor productivity growth &      2.35 &      0.95 \\  
Inflation Rate &      3.54 &      4.47 \\  \hline

@@

Share of Priv. Consumption &     63.06 &     62.56 \\  
Share of Investment &     26.46 &     22.24 \\  
Share of Gov. Consumption &     16.75 &     15.84 \\  
Share of Imports &     21.77 &     22.24 \\  
Share of Exports &     15.50 &     22.87 \\  
Employment Share &     38.77 &     41.69 \\  
Labor productivity growth &      1.44 &      1.09 \\  
Inflation Rate &     14.70 &     14.71 \\    \hline

@@

Share of Imports &     52.85 &     30.59 \\  
Share of Exports &     51.30 &     34.67 \\  

@@

Labor productivity growth &      3.44 &      2.02 \\  
Inflation Rate &      8.36 &     47.41 \\   \hline

@@

Share of Priv. Consumption &     59.00 &     57.32 \\  

@@

Share of Gov. Consumption &     17.55 &     18.87 \\  
Share of Imports &     19.28 &     19.88 \\  
Share of Exports &     19.86 &     19.22 \\  
Employment Share &     38.25 &     44.13 \\  
Labor productivity growth &      2.16 &      1.23 \\  
Inflation Rate &      9.48 &     12.94 \\  \hline

@@

Share of Priv. Consumption &     48.16 &     55.38 \\  
Share of Investment &     22.57 &     26.28 \\  
Share of Gov. Consumption &     15.33 &     22.74 \\  
Share of Imports &     81.83 &     35.72 \\  
Share of Exports &     95.78 &     40.11 \\  
Employment Share &     46.63 &     45.79 \\  
Labor productivity growth &      1.91 &      1.41 \\  
Inflation Rate &      4.61 &     35.04 \\  \hline

@@

Share of Priv. Consumption &     50.90 &     54.79 \\  
Share of Investment &     22.62 &     26.17 \\  
Share of Gov. Consumption &     21.94 &     18.39 \\  
Share of Imports &     47.47 &     38.28 \\  
Share of Exports &     52.01 &     37.62 \\  

@@

Labor productivity growth &      1.45 &      1.40 \\  
Inflation Rate &      4.18 &     12.26 \\  \hline

@@

Share of Priv. Consumption &     66.93 &     65.47 \\  
Share of Investment &     26.93 &     21.34 \\  
Share of Gov. Consumption &     14.03 &     13.93 \\  
Share of Imports &     31.16 &     21.09 \\  
Share of Exports &     23.27 &     21.83 \\  
Employment Share &     41.81 &     38.56 \\  
Labor productivity growth &      1.95 &      1.24 \\  
Inflation Rate &     14.14 &     19.60 \\   \hline

@@

Share of Priv. Consumption &     63.12 &     63.00 \\  
Share of Investment &     23.78 &     22.13 \\  
Share of Gov. Consumption &     14.51 &     15.26 \\  
Share of Imports &     18.55 &     17.59 \\  
Share of Exports &     17.13 &     17.97 \\  
Employment Share &     35.38 &     42.17 \\  
Labor productivity growth &      2.55 &      1.07 \\  
Inflation Rate &      9.87 &     14.12 \\  \hline

@@

\annote{Predictors' means for each country and its doppelgangers during the pre-treatment period. The doppelganger column corresponds to a simple (non-weighted) average and thus some discrepancies may arise because of that. All numbers are in percent. Variables definitions can be found in Table \ref{TA_Description}.}

@@

\section{\label{SS_Components} Components Analysis}

\begin{figure}[h!]
    \centering
    \caption{\label{F_Components_AUT} Components of Austria's GDP}
    \subfigure[Private Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_c_1_Annual.eps}}
    \subfigure[Government Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_g_1_Annual.eps}}
    \subfigure[Investment]{\includegraphics[width=8cm]{Composition/SCM_csh_i_1_Annual.eps}}
    \subfigure[Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_x_1_Annual.eps}}
    \subfigure[Imports]{\includegraphics[width=8cm]{Composition/SCM_csh_m_1_Annual.eps}}
    \subfigure[Net Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_nx_1_Annual.eps}}
    \annote{The plots depict, for each GDP component, the deviation in percent from the value of 1970. The blue dashed lines represents the synthetic Austria computed in section \ref{S_Doppelganger}. The full black lines stand for the actual Austrian series. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession.}
\end{figure}

\begin{figure}[h!]
    \centering
    \caption{\label{F_Components_BEL} Components of Belgium's GDP}
    \subfigure[Private Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_c_3_Annual.eps}}
    \subfigure[Government Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_g_3_Annual.eps}}
    \subfigure[Investment]{\includegraphics[width=8cm]{Composition/SCM_csh_i_3_Annual.eps}}
    \subfigure[Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_x_3_Annual.eps}}
    \subfigure[Imports]{\includegraphics[width=8cm]{Composition/SCM_csh_m_3_Annual.eps}}
    \subfigure[Net Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_nx_3_Annual.eps}}
    \annote{The plots depict, for each GDP component, the deviation in percent from the value of 1970. The blue dashed lines represents the synthetic Austria computed in section \ref{S_Doppelganger}. The full black lines stand for the actual Belgian series. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. }
\end{figure}

\begin{figure}[h!]
    \centering
    \caption{\label{F_Components_FIN} Components of Finland's GDP}
    \subfigure[Private Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_c_7_Annual.eps}}
    \subfigure[Government Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_g_7_Annual.eps}}
    \subfigure[Investment]{\includegraphics[width=8cm]{Composition/SCM_csh_i_7_Annual.eps}}
    \subfigure[Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_x_7_Annual.eps}}
    \subfigure[Imports]{\includegraphics[width=8cm]{Composition/SCM_csh_m_7_Annual.eps}}
    \subfigure[Net Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_nx_7_Annual.eps}}
    \annote{The plots depict, for each GDP component, the deviation in percent from the value of 1970. The blue dashed lines represents the synthetic Belgium computed in section \ref{S_Doppelganger}. The full black lines stand for the actual Finnish series. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. }
\end{figure}

\begin{figure}[h!]
    \centering
    \caption{\label{F_Components_FRA} Components of France's GDP}
    \subfigure[Private Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_c_8_Annual.eps}}
    \subfigure[Government Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_g_8_Annual.eps}}
    \subfigure[Investment]{\includegraphics[width=8cm]{Composition/SCM_csh_i_8_Annual.eps}}
    \subfigure[Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_x_8_Annual.eps}}
    \subfigure[Imports]{\includegraphics[width=8cm]{Composition/SCM_csh_m_8_Annual.eps}}
    \subfigure[Net Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_nx_8_Annual.eps}}
    \annote{The plots depict, for each GDP component, the deviation in percent from the value of 1970. The blue dashed lines represents the synthetic France computed in section \ref{S_Doppelganger}. The full black lines stand for the actual French series. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. }
\end{figure}

\begin{figure}[h!]
    \centering
    \caption{\label{F_Components_DEU} Components of Germany's GDP}
    \subfigure[Private Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_c_9_Annual.eps}}
    \subfigure[Government Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_g_9_Annual.eps}}
    \subfigure[Investment]{\includegraphics[width=8cm]{Composition/SCM_csh_i_9_Annual.eps}}
    \subfigure[Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_x_9_Annual.eps}}
    \subfigure[Imports]{\includegraphics[width=8cm]{Composition/SCM_csh_m_9_Annual.eps}}
    \subfigure[Net Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_nx_9_Annual.eps}}
    \annote{The plots depict, for each GDP component, the deviation in percent from the value of 1970. The blue dashed lines represents the synthetic Germany computed in section \ref{S_Doppelganger}. The full black lines stand for the actual German series. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. }
\end{figure}

\begin{figure}[h!]
    \centering
    \caption{\label{F_Components_GRC} Components of Greece's GDP}
    \subfigure[Private Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_c_10_Annual.eps}}
    \subfigure[Government Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_g_10_Annual.eps}}
    \subfigure[Investment]{\includegraphics[width=8cm]{Composition/SCM_csh_i_10_Annual.eps}}
    \subfigure[Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_x_10_Annual.eps}}
    \subfigure[Imports]{\includegraphics[width=8cm]{Composition/SCM_csh_m_10_Annual.eps}}
    \subfigure[Net Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_nx_10_Annual.eps}}
    \annote{The plots depict, for each GDP component, the deviation in percent from the value of 1970. The blue dashed lines represents the synthetic Greece computed in section \ref{S_Doppelganger}. The full black lines stand for the actual Greek series. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. }
\end{figure}

\begin{figure}[h!]
    \centering
    \caption{\label{F_Components_IRL} Components of Ireland's GDP}
    \subfigure[Private Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_c_12_Annual.eps}}
    \subfigure[Government Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_g_12_Annual.eps}}
    \subfigure[Investment]{\includegraphics[width=8cm]{Composition/SCM_csh_i_12_Annual.eps}}
    \subfigure[Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_m_12_Annual.eps}}
    \subfigure[Imports]{\includegraphics[width=8cm]{Composition/SCM_csh_x_12_Annual.eps}}
    \subfigure[Net Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_nx_12_Annual.eps}}
    \annote{The plots depict, for each GDP component, the deviation in percent from the value of 1970. The blue dashed lines represents the synthetic Ireland computed in section \ref{S_Doppelganger}. The full black lines stand for the actual Irish series. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. }
\end{figure}

\begin{figure}[h!]
    \centering
    \caption{\label{F_Components_ITA} Components of Italy's GDP}
    \subfigure[Private Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_c_14_Annual.eps}}
    \subfigure[Government Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_g_14_Annual.eps}}
    \subfigure[Investment]{\includegraphics[width=8cm]{Composition/SCM_csh_i_14_Annual.eps}}
    \subfigure[Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_m_14_Annual.eps}}
    \subfigure[Imports]{\includegraphics[width=8cm]{Composition/SCM_csh_x_14_Annual.eps}}
    \subfigure[Net Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_nx_14_Annual.eps}}
    \annote{The plots depict, for each GDP component, the deviation in percent from the value of 1970. The blue dashed lines represents the synthetic Italy computed in section \ref{S_Doppelganger}. The full black lines stand for the actual Italian series. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. }
\end{figure}

\begin{figure}[h!]
    \centering
    \caption{\label{F_Components_LUX} Components of Luxembourg's GDP}
    \subfigure[Private Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_c_16_Annual.eps}}
    \subfigure[Government Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_g_16_Annual.eps}}
    \subfigure[Investment]{\includegraphics[width=8cm]{Composition/SCM_csh_i_16_Annual.eps}}
    \subfigure[Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_x_16_Annual.eps}}
    \subfigure[Imports]{\includegraphics[width=8cm]{Composition/SCM_csh_m_16_Annual.eps}}
    \subfigure[Net Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_nx_16_Annual.eps}}
    \annote{The plots depict, for each GDP component, the deviation in percent from the value of 1970. The blue dashed lines represents the synthetic Luxembourg computed in section \ref{S_Doppelganger}. The full black lines stand for the actual Luxembourg's series. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession. }
\end{figure}

\begin{figure}[h!]
    \centering
    \caption{\label{F_Components_NLD} Components of The Netherlands's GDP}
    \subfigure[Private Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_c_18_Annual.eps}}
    \subfigure[Government Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_g_18_Annual.eps}}
    \subfigure[Investment]{\includegraphics[width=8cm]{Composition/SCM_csh_i_18_Annual.eps}}
    \subfigure[Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_x_18_Annual.eps}}
    \subfigure[Imports]{\includegraphics[width=8cm]{Composition/SCM_csh_m_18_Annual.eps}}
    \subfigure[Net Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_nx_18_Annual.eps}}
    \annote{The plots depict, for each GDP component, the deviation in percent from the value of 1970. The blue dashed lines represents the synthetic Netherlands computed in section \ref{S_Doppelganger}. The full black lines stand for the actual Dutch series. The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession.}
\end{figure}

\begin{figure}[h!]
    \centering
    \caption{\label{F_Components_PRT} Components of Portugal's GDP}
    \subfigure[Private Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_c_21_Annual.eps}}
    \subfigure[Government Consumption]{\includegraphics[width=8cm]{Composition/SCM_csh_g_21_Annual.eps}}
    \subfigure[Investment]{\includegraphics[width=8cm]{Composition/SCM_csh_i_21_Annual.eps}}
    \subfigure[Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_x_21_Annual.eps}}
    \subfigure[Imports]{\includegraphics[width=8cm]{Composition/SCM_csh_m_21_Annual.eps}}
    \subfigure[Net Exports]{\includegraphics[width=8cm]{Composition/SCM_csh_nx_21_Annual.eps}}
    \annote{The plots depict, for each GDP component, the deviation in percent from the value of 1970. The blue dashed lines represents the synthetic Portugal computed in section \ref{S_Doppelganger}. The full black lines stand for the actual Portuguese series.  The shaded area corresponds to two standard deviations of the difference between the treated country and the doppelganger prior to the euro accession.}
\end{figure}
